Action alternatives & disruption factor

### 2023-08-11 01_studies/01_Laborstudie ProVisioNET/R script/action alternatives/action_alternatives_confidence_factor.Rmd
update disruption

---
title: "Action alternatives & confidence factor"
output: html_document
date: "2023-03-28"
---

@@

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, event, confidence_factor) %>% 
  filter(!ID %in% c(141,
                    142,
                    204,
                    226), # filter relevant rows
         event %in% c("chatting")) %>%
  janitor::clean_names()

@@

# descriptives & plots
```{r}
# confidence factor
describeBy(main$confidence_factor, main$id)
plot_confi <- boxplot(confidence_factor ~ id, data = main)

# # sjt cm
# describeBy(main$sjt, main$id)
# plot_confi <- boxplot(sjt ~ id, data = main)

@@

# confidence factor x count of action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Count of action alternatives") +
  theme_cowplot()

@@

# confidence factor x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(confidence_factor) | !is.na(percent_nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = confidence_factor,
                       y = percent_nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "Confidence Factor",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

@@

#### confidence factor
# t-test for expertise differences
t.test(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$confidence_factor[main$id == "Expert"],
       y = main$confidence_factor[main$id == "Novice"],
       na.rm = TRUE)

@@

# Subset anlegen nur mit Variablen
main %>% 
  select(confidence_factor, 
         count, 
         nd,
         percent_nd) -> corr_subset

@@

# novices: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

nov_confi_count_corr <- cor.test(corr.nov$confidence_factor, 
                                 corr.nov$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(nov_confi_count_corr, 
      short = F)

# experts: correlation between confidence factor and count
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

exp_confi_count_corr <- cor.test(corr.exp$confidence_factor, 
                                 corr.exp$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(exp_confi_count_corr, 
      short = F)

# full sample: correlation between confidence factor and count
full_confi_count_corr <- corr.test(main$confidence_factor, 
                                   main$count, 
                                   method=c("pearson"), 
                                   adjust="holm")
print(full_confi_count_corr,
      short = F)

@@

# novices: correlation between confidence factor and non-disruptive alternatives (absolute score)
nov_confi_abs.nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_abs.nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives (absolute score)
exp_confi_abs.nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_abs.nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
full_confi_abs.nd_corr <- corr.test(main$confidence_factor, 
                                main$nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_abs.nd_corr,
      short = F)

@@

# novices: correlation between confidence factor and non-disruptive alternatives (relative score)
nov_confi_nd_corr <- cor.test(corr.nov$confidence_factor,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_confi_nd_corr, 
      short = F)

# experts: correlation between confidence factor and non-disruptive alternatives (relative score)
exp_confi_nd_corr <- cor.test(corr.exp$confidence_factor,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_confi_nd_corr,
      short = F)

# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
full_confi_nd_corr <- corr.test(main$confidence_factor, 
                                main$percent_nd, method=c("pearson"),
                                adjust="holm")
print(full_confi_nd_corr,
      short = F)

@@

# full sample: correlation between confidence factor and non-disruptive alternatives (absolute score)
full_count_abs.nd_corr <- corr.test(main$count, 
                                main$nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_abs.nd_corr,
      short = F)

@@

# full sample: correlation between confidence factor and non-disruptive alternatives (relative score)
full_count_nd_corr <- corr.test(main$count, 
                                main$percent_nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)

>>>>

---
title: "Action alternatives & disruption factor"
output: html_document
date: "2023-03-28"
---

@@

# SELF-REPORT DATA
df_sri <- 
  excel_sheets("data/coding_sri.xlsx") %>% 
  map_df(~read_xlsx("data/coding_sri.xlsx",.)) %>% 
  dplyr::select(ID, event, disruption_factor) %>% 
  filter(!ID %in% c(141,
                    142,
                    204,
                    226), # filter relevant rows
         event %in% c("chatting")) %>%
  janitor::clean_names()

@@

# descriptives & plots
```{r}
# disruption factor
describeBy(main$disruption_factor, main$id)
plot_disrup <- boxplot(disruption_factor ~ id, data = main)

# # sjt cm
# describeBy(main$sjt, main$id)
# plot_disrup <- boxplot(sjt ~ id, data = main)

@@

# disruption factor x count of action alternatives
```{r}
main %>% 
  filter(!is.na(disruption_factor) | !is.na(count)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = disruption_factor,
                       y = count,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "disruption Factor",
       y = "Count of action alternatives") +
  theme_cowplot()

@@

# disruption factor x non-disruptive action alternatives
```{r}
main %>% 
  filter(!is.na(disruption_factor) | !is.na(percent_nd)) %>% 
  # filter(id %in% c("Novice")) %>% 
  ggplot(mapping = aes(x = disruption_factor,
                       y = percent_nd,
                       colour = id
                       )
         ) +
  geom_point() + 
  geom_smooth(method = "lm",
              se = TRUE) +
  scale_color_viridis_d() +
  labs(x = "disruption Factor",
       y = "Non-disruptive action alternatives") + 
  theme_cowplot()

@@

#### disruption factor
# t-test for expertise differences
t.test(x = main$disruption_factor[main$id == "Expert"],
       y = main$disruption_factor[main$id == "Novice"])

# effect size for expertise differences
CohenD(x = main$disruption_factor[main$id == "Expert"],
       y = main$disruption_factor[main$id == "Novice"],
       na.rm = TRUE)

@@

# Subset anlegen nur mit Variablen
main %>% 
  select(disruption_factor, 
         count, 
         nd,
         percent_nd) -> corr_subset

@@

# novices: correlation between disruption factor and count
main %>% 
  filter(id %in% c("Novice")) -> corr.nov

nov_disrup_count_corr <- cor.test(corr.nov$disruption_factor, 
                                 corr.nov$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(nov_disrup_count_corr, 
      short = F)

# experts: correlation between disruption factor and count
main %>% 
  filter(id %in% c("Expert")) -> corr.exp

exp_disrup_count_corr <- cor.test(corr.exp$disruption_factor, 
                                 corr.exp$count, 
                                 method=c("pearson"),
                                 adjust="holm")
print(exp_disrup_count_corr, 
      short = F)

# full sample: correlation between disruption factor and count
full_disrup_count_corr <- corr.test(main$disruption_factor, 
                                   main$count, 
                                   method=c("pearson"), 
                                   adjust="holm")
print(full_disrup_count_corr,
      short = F)

@@

# novices: correlation between disruption factor and non-disruptive alternatives (absolute score)
nov_disrup_abs.nd_corr <- cor.test(corr.nov$disruption_factor,
                              corr.nov$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_disrup_abs.nd_corr, 
      short = F)

# experts: correlation between disruption factor and non-disruptive alternatives (absolute score)
exp_disrup_abs.nd_corr <- cor.test(corr.exp$disruption_factor,
                              corr.exp$nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_disrup_abs.nd_corr,
      short = F)

# full sample: correlation between disruption factor and non-disruptive alternatives (absolute score)
full_disrup_abs.nd_corr <- corr.test(main$disruption_factor, 
                                main$nd, method=c("pearson"),
                                adjust="holm")
print(full_disrup_abs.nd_corr,
      short = F)

@@

# novices: correlation between disruption factor and non-disruptive alternatives (relative score)
nov_disrup_nd_corr <- cor.test(corr.nov$disruption_factor,
                              corr.nov$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(nov_disrup_nd_corr, 
      short = F)

# experts: correlation between disruption factor and non-disruptive alternatives (relative score)
exp_disrup_nd_corr <- cor.test(corr.exp$disruption_factor,
                              corr.exp$percent_nd, 
                              method=c("pearson"),
                              adjust="holm")
print(exp_disrup_nd_corr,
      short = F)

# full sample: correlation between disruption factor and non-disruptive alternatives (relative score)
full_disrup_nd_corr <- corr.test(main$disruption_factor, 
                                main$percent_nd, method=c("pearson"),
                                adjust="holm")
print(full_disrup_nd_corr,
      short = F)

@@

# full sample: correlation between disruption factor and non-disruptive alternatives (absolute score)
full_count_abs.nd_corr <- corr.test(main$count, 
                                main$nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_abs.nd_corr,
      short = F)

@@

# full sample: correlation between disruption factor and non-disruptive alternatives (relative score)
full_count_nd_corr <- corr.test(main$count, 
                                main$percent_nd, 
                                method=c("pearson"),
                                adjust="holm")
print(full_count_nd_corr,
      short = F)
